Manuscript Title

### 2024-03-06 manuscript/_manuscript-template.qmd
update manuscript template

>>>>

---
title: "Manuscript Title"
authors:
  - name: Jane Doe
    email: "janedoe@mockuniversity.edu"
    affiliations:
      - name: University of Mock 
        department: Department of Something 
        city: Miami
        state: Florida
        country: United States
  - name: Author 2
    email: "xxxxxx"
    affiliations:
      - name: xxxxx
        department: xxxxxx
        city: xxxxx
        state: xxxxx
        country: xxxxxx
  - name: Additional Co-author(s)
    email: "xxxxxxx"
    affiliations:
      - name: xxxxx
        department: xxxxxx
        city: xxxx
        state: xxxxx
        country: xxxxxx

abstract: |
  The is the abstract section.  Ipsum leo porta – lacinia sed ac interdum nec vel ad. Elementum augue platea eleifend himenaeos nisl, viverra sem molestie. Hendrerit enim torquent litora fusce ultrices, magna, lacus id potenti! Imperdiet vulputate etiam conubia sem mi incep- tos. Quisque mollis viverra lacinia bibendum ultricies, dui est gravida tristique nascetur. Pellentesque id elementum com- modo pretium quisque purus mi taciti.

index-terms: 
  - Keyword 1
  - Keyword 2 
  - Keyword 3
  - Keyword 4
  - Keyword 5

format:
  ieee-typst: default
bibliography: references.bib
---
```{r}
#| echo: FALSE
library(lorem)
```

## Introduction
_Introduce the research topic, state the research problem, and outline the study's objectives. Provide background information to set the context. This is an exmaple in-text citation_ @netwok2020.
`r lorem::ipsum(paragraphs = 3)`

## Results

```{r}
#| echo: FALSE
#| output: FALSE

# This is an example of a basic analysis code chunk
## Load necessary libraries
library(ggplot2)

## Simple linear regression analysis with 'mtcars' dataset
lm_model <- lm(mpg ~ wt, data = mtcars)

## Summary of the linear model
summary(lm_model)

```{r, broomoutput}
#| echo: FALSE

## Using broom to tidy the regression model results for presentation in-text
library(broom)

library(broom)

# Tidy the regression model output for easy access to coefficients
tidy_lm <- broom::tidy(lm_model)

# Round the coefficients to 2 decimal places
tidy_lm$estimate <- round(tidy_lm$estimate, 2)
tidy_lm$std.error <- round(tidy_lm$std.error, 2)
tidy_lm$statistic <- round(tidy_lm$statistic, 2)
tidy_lm$p.value <- round(tidy_lm$p.value, 2)

# Extract the rounded coefficient and p-value for 'wt'
wt_coefficient <- tidy_lm$estimate[2] # The coefficient of 'wt', rounded to 2 decimal places
wt_pvalue <- tidy_lm$p.value[2] # The p-value for the 'wt' coefficient, rounded to 2 decimal places

# Glance at the model's summary statistics to get R-squared and round it
model_summary <- broom::glance(lm_model)

# Round the summary statistics to 2 decimal places
model_summary$r.squared <- round(model_summary$r.squared, 2)
model_summary$statistic <- round(model_summary$statistic, 2)
model_summary$p.value <- round(model_summary$p.value, 2)

# Assign the rounded values to variables
r_squared <- model_summary$r.squared # R-squared value, rounded to 2 decimal places
f_statistic <- model_summary$statistic # F-statistic, rounded to 2 decimal places
model_pvalue <- model_summary$p.value # Model p-value, rounded to 2 decimal places

The regression analysis revealed that for every additional 1,000 pounds of weight, the car's miles per gallon decreases by an average of `r wt_coefficient` units (p = `r wt_pvalue`). This model explains `r r_squared`% of the variance in fuel efficiency, indicating a strong relationship between car weight and mpg. The model's F-statistic is `r f_statistic`, with a p-value of `r model_pvalue`, demonstrating the statistical significance of the regression model.

The following portion of code [geom_smooth()` using formula = 'y ~ x'] still shows in the rendered text even though I have set `#| echo: FALSE`.
```{r, fig.width=4, fig.height=4}
#| echo: FALSE

# This is an example of a basic scatterplot of the regression analysis.

ggplot(mtcars, aes(x = wt, y = mpg)) +
    geom_point() +
    geom_smooth(method = "lm", col = "blue") +
    labs(title = "MPG vs. Car Weight", x = "Weight (1000 lbs)", y = "Miles per Gallon") +
    theme_minimal()

```{r, fig.width=4, fig.height=4}
#| echo: FALSE

# This is an example of a diagnostic plot of the regression analysis.

par(mfrow = c(2, 2)) # Arrange plots in a 2x2 grid
plot(lm_model)

### [Subsection Title]
_Present additional findings related to a particular aspect of the study, supported by data._
`r lorem::ipsum(paragraphs = 1)`

#########
#########
#########
